%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Engineering Project}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Side Project} % Organization
    {Raspberry Pi Cluster} % Title
    {} % Location
    {Sep. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built a cluster with 4 Raspberry Pis with a self-made efficient script which can quickly apply popular ecosystem like Hadoop, Spark.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Piece Work} % Organization
    {Leapsy AR Glasses Video Stream Pan/Tilt Head} % Title
    {} % Location
    {Jul. 2017 - Oct. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {I collected sensor data on Android-based AR Glasses to capture current attitude and sent it back to Raspberry Pi to synchronize camera pan/tilt head’s direction then return video stream back to glasses through Wi-Fi.}
        \item {I made pan/tilt head structure using 3D print model to contain camera and two servo motors, and designed the power supply circuit for both motors and Raspberry Pi.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Undergraduate Project} % Organization
    {Modularized Quadcopter Architecture with Computer Vision Control} % Title
    {} % Location
    {Apr. 2016 - Sep. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built a quadcopter from scratch, including motors, sensors, power circuits, etc.}
        \item {Used PID for balancing algorithm on the control board and object detection with OpenCV on the CV board.}
        \item {Got honorable award at HOLTEK MCU Design Contest 2016 and Top 10 at ARM Design Contest 2016.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
