%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experiences}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Data \& Applied Scientist} % Job title
    {Microsoft STCA Bing Multimedia} % Organization
    {Suzhou, Jiangsu, China} % Location
    {Jul. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        % Core Priorities:
        \item {Provide better video recommendation qualities to increase user click-through rates and daily active users on different scenarios like Bing, MSN, and Edge.}
        % \item {Shipped \textbf{Relevance Model} on MSN Article (Defect Rate reduces from 5.9\% to 5\%, Relevance grows from 35.2 to 50 pts), Bing Super Caption (Video-Triggered Pane-CTR grows from 2.0\% to 3.0\%), and Edge Underside (Video-Triggered Pane-CTR gros from 0.75\% to 1.2\%).}
        \item {Shipped \textbf{Relevance Model} to control the relevance quality while increasing coverage, which has \textbf{2.2\% defect rate reduction}, in several related video scenarios like MSN Article, Bing Super Caption, and Edge Underside.}
        % TODO: training data amount? training strategy: negative sampling? features: text feature? offline and online measurement: precision, recall, defect rate.
        \item {Shipped \textbf{CTR Model} on MSN Article with \textbf{Video-CI/UU +2.4\%} and \textbf{Video-CI Ratio +2.33\%} on 37 markets.}
        % TODO: training data amount? training strategy: daily aggregation, top features: engagement feature, relevance feature? offline and online measurement: DCG, gDCG, defect rate, CI.
        \item {To \textit{increase development efficiency}, made an online \textbf{Related Video Debug Tool} and general utilities such as general data processing modules, fully automatic annotation pipeline, config visualization script.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Algorithm Intern} % Job title
    {Microsoft STCA Bing NLP Carina} % Organization
    {Beijing, China} % Location
    {Jul. 2020 - Jun. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built a \textbf{Numeric Information Extraction System} for financial reports. Designed annotation guideline, trained MRC-based Sequence Labeling, and built back-end API services with docker containers.}
        \item {Built models of the \textbf{AI Writer} for automatic article generation and rewriting by generation models and information retrieval methods.}
        % TODO: GPT-2, Back-Translation, ...
        % \item {Built models of \textbf{Writing Assistant} which offers such as copyediting, typesetting, proofreading, indexing, page makeup.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Intern} % Job title
    {Microsoft Research Asia Knowledge Computing} % Organization
    {Beijing, China} % Location
    {Dec. 2019 - May. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        % \href{https://www.bilibili.com/video/BV1fV411q7Ho/}{Microsoft's Bilibili}
        % \item {Academic research on how to generate slides from academic papers. Got published in AAAI 2021, and do a live sharing on Microsoft's Bilibili.}
        \item {Academic research on how to generate slides from academic papers. Got published to AAAI 2021, and do a live sharing on \href{https://www.bilibili.com/video/BV1fV411q7Ho/}{Microsoft's Bilibili}.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
