%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Algorithm Intern} % Job title
    {Microsoft Search Technology Center Asia Carina Group} % Organization
    {} % Location
    {Jul. 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {AI Writer for automatic article generation and rewriting by generation models and information retrieval methods.}
        \item {Writing Assistant which offers such as copyediting, typesetting, proofreading, indexing, page makeup.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Intern} % Job title
    {Microsoft Research Asia Knowledge Computing Group} % Organization
    {} % Location
    {Dec. 2019 - May. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Generation of slides from academic paper.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Intern} % Job title
    {Peking University National Engineering Research Center of Software Engineering} % Organization
    {} % Location
    {Jul. 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Doing case of Anti-healthcare fraud and Medical record analysis.}
        \item {Including research of Knowledge Extraction, Knowledge Graph}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Embedding System Design Software Intern} % Job title
    {Taiwan Industrial Technology Research Institute} % Organization
    {} % Location
    {Jul. 2016 - Aug. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {In the self-driving group, I mainly handled the STV0991 development board which was going to carry the computer vision algorithms.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
