%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Project}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {ACL (The Association for Computational Linguistics) in Progress} % Organization
    {GCAKE: Graph and Context Attentional Knowledge Embedding} % Title
    {} % Location
    {Oct. 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {A knowledge graph representation learning using self-attention (a Transformer like architecture) encoded context not only between triples but also considered the description context and graph structure.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {WWW (The Web Conference) under Review} % Organization
    {Similar Cases Recommendation via Legal Knowledge Graph Construction and Representation} % Title
    {} % Location
    {Aug. 2019 - Oct. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Propose a pipeline from raw lawsuit case into dense representation to compare and recommend the top k most similar cases.}
        \item {Including subtask of Named-entity Recognition, Relation Extraction, Knowledge Graph Embedding. Using jointly-trained multitask model of fine-tuned BERT.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Online Course} % Organization
    {Stanford CS224n: Natural Language Processing with Deep Learning} % Title
    {} % Location
    {Jul. 2019 - Nov. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {To review the detail learned from the last two semesters.}
        \item {Project including Neural Dependency Parsing, Neural Machine Translation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Kaggle Competition} % Organization
    {Jigsaw Unintended Bias in Toxicity Classification} % Title
    {} % Location
    {Feb. 2019 - May. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {This competition is aim to classify whether a comments is toxic. Our team design different models such as BERT, ELMo etc. as classifier and finally ensemble them. Our team reach Top 1\% in rank.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Course Project} % Organization
    {SemEval-2013 Task 13: Word Sense Induction for Graded and Non-Graded Senses} % Title
    {} % Location
    {Jun. 2019 - Jul. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {This task is word disambiguation. Determine a meaning of a word in different sentences. There are two subtask, one is finding the closest WordNet lemma, another is clustering between sentences.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Course Project} % Organization
    {SemEval-2018 Task 7: Semantic Relation Extraction and Classification in Scientific Papers} % Title
    {} % Location
    {May. 2019 - Jun. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {This task is the relation classification task. The scenario is based on the abstract of lots of papers. For each sentence, given two entities, and we have to determine which relation might between the entities.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Course Project} % Organization
    {Chinese Word Segment, Part-of-speech Tagging Named-entity Recognition} % Title
    {} % Location
    {Apr. 2019 - May. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {The classic Chinese sequence labeling tasks. I used the BiLSTM-CRF model as the main approach compare with other baselines.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Digital China Innovation Contest 2019} % Organization
    {Failure Prediction of Concrete Piston for Concrete Pump Vehicles} % Title
    {} % Location
    {Jan. 2019 - Mar. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {In this competition, each sample is a time-series data of a concrete pump vehicle. The goal is to predict the likelihood of each data sequence that whether a machine might fail. I used LightGBM and reach Top 5\% in rank.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Course Project / National Taiwan University 2048 BOT Competition in 2014} % Organization
    {AI BOT of the Game 2048 using MCTS and Reinforcement Learning} % Title
    {} % Location
    {Nov. 2018 - Dec. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {In 2014, I and my friend Tom used MCTS with alpha-beta purning to select best action. And score each state(board) with our own designed evaluation function.}
        \item {In 2018, I built a Reinforcement Learning model and test performance between Policy Gradient and Deep Q-Learning.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
